---
title: "QMM bpalazzo_6"
author: "Brandon Palazzo"
date: "10/12/2020"
output:
  pdf_document: default
  html_document: default
---

Load lpSolveAPI Library
```{r}
library(lpSolveAPI)
```

Read LP File

LP File:

/* Objective function */
min: 22 A1 + 14 A2 + 30 A3 + 16 B1 + 20 B2 + 24 B3 + 600 A1 + 600 A2 + 600 A3 + 625 B1 + 625 B2 + 625 B3;


/* Constraints */

Monthly_Demand_Warehouse1: A1 + B1  >= 80;
Monthly_Demand_Warehouse2: A2 + B2  >= 60;
Monthly_Demand_Warehouse3: A3 + B3  >= 70;

Monthly_ProdCap_PlantA: A1 + A2 + A3  <= 100;
Monthly_ProdCap_PlantB: B1 + B2 + B3  <= 120;
```{r}
x <- read.lp("QMM bpalazzo_6.lp") 
x

```
Solve for X

```{r}
solve(x)
```

Solve for the objectives, variables, and constraints
```{r}
get.objective(x)        
get.variables(x)       
get.constraints(x)      

```

Amounts each warehouse and plant should produce:

Plant A, W1 = 0
Plant A, W2 = 60
Plant A, W3 = 40
Plant B, W1 = 80
Plant B, W2 = 0
Plant B, W3 = 30






